Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-06 thesis/paper.tex
Added rqs to results

\subsection{RQ1 Results} \label{results_rq1}
%Add a small introductory sentence to this paragraph and have it as the first paragraph of this section (Don't forget to ref the table)
Many changes were found between version 1.4 and version 2.0. Initial inspection revealed there to be many deprecations which were later re-implemented as new modules. We have considered these changes as a single change instead of a deprecation and a re-implementation. In total, thirteen unique changes were found. These changes are show in table \ref{table:Categories}.
%
The changes have been divided up into four specific categories, namely: new, modified, removed and general trends. The category new concerns additions of modules, modified concerns modifications to modules that existed in version 1.4 and removed are changes where functionality was removed being deprecated or replaced by functionality. General trends are broad changes that do not directly affect functionality. 
%%Add percentages for both main and sub and specify which is for which
After cross-examining our results with the interviewee and their responses, we found that 78\% of our main categorisation predictions matched the actual intent of the changes and that 78\% of our sub categorisations predictions matched the actual intents.

@@

\subsection{RQ2 Results} \label{results_rq2}
The results related to \textbf{RQ2} are structured around each of Lehman's laws of software evolution \cite{lehman1980programs} and to what extent our findings show that the laws apply to platform APIs. A summary of our findings can be seen in Table \ref{table:lehman}.

>>>>

\subsection{RQ1 Results} \label{results_rq1}
\noindent
RQ1: \textbf{How do companies actively drive API evolution?}

\noindent
RQ1.1: \textbf{To what extent can we reverse engineer API change decisions?}
\smallskip

Many changes were found between version 1.4 and version 2.0. Initial inspection revealed there to be many deprecations which were later re-implemented as new modules. We have considered these changes as a single change instead of a deprecation and a re-implementation. In total, thirteen unique changes were found. These changes are show in table \ref{table:Categories}.
%
The changes have been divided up into four specific categories, namely: new, modified, removed and general trends. The category new concerns additions of modules, modified concerns modifications to modules that existed in version 1.4 and removed are changes where functionality was removed being deprecated or replaced by functionality. General trends are broad changes that do not directly affect functionality. 
%%Add percentages for both main and sub and specify which is for which
After cross-examining our results with the interviewee and their responses, we found that 78\% of our main categorisation predictions matched the actual intent of the changes and that 78\% of our sub categorisations predictions matched the actual intents.

@@

\subsection{RQ2 Results} \label{results_rq2}
\noindent
RQ2: \textbf{How do APIs ``passively'' evolve?}
\smallskip

The results related to \textbf{RQ2} are structured around each of Lehman's laws of software evolution \cite{lehman1980programs} and to what extent our findings show that the laws apply to platform APIs. A summary of our findings can be seen in Table \ref{table:lehman}.
